Manuscript_Github_ancestral_pir_210801

### 2021-09-21 AncestralPir/AnalysisCode/Manuscript_Github_AncestralPir.Rmd
Save phylo anc plot
Delete superfluous phylo tree

```{r tree_heatmap_all-genes}

ancestral_df <- bind_rows(cyno_percentile_all,
                          ovale_percentile_all,
                          cb_percentile_all,
                          vinck_percentile_all,
                          coat_percentile_all,
                          yoel_percentile_all,
                          berg_percentile_all,
                          chab_percentile_all,
                          vivax_percentile_all)
ancestral_data <- lapply(phylog$old.tip.label, function(id){
  #If any of the pattern is in the string one will be TRUE
  ratio <- if(any(str_detect(string = paste(id), 
                             pattern = ancestral_df$Geneid))){
    index_id <- str_detect(string = paste(id), 
                           pattern = ancestral_df$Geneid)
    ancestral_df$percentile[index_id]*100
  }else{
    NA
  }
  return(list(ratio = ratio))
}) %>% 
  bind_rows
ancestral_data <- as.data.frame(ancestral_data)

rownames(ancestral_data) <- phylog$tip.label

breaks <- seq(0, 100, by = 10)

(tr <- ggtree(phylog, 
            branch.length = 'none',
            layout = 'circular') +
  geom_tiplab2(aes(angle=angle, x = x + 2.5), 
               cex = 3, 
               color='black',
               font = 3) +
  ggplot2::xlim(0,20) 
)
```

@@

p
```

>>>>

@@

if(global_save_var){
  ggsave('plots/thesis_chapter3_figure_ancPhyloHeatmap.png',
         width = 7,
         height = 5,
         units = "in",
         p)
}
```
